\input{resume}
\begin{document}

\contactinformation{Software Engineer}

\begin{concept}{Education}
\data{MSc in Applied Mathematics on Combinatorial Algorithms, University of Chile.}{Chile, 2022 - 2023}
\data{BSc in Mathematics and Computer Science Engineering, École CentralSupélec.}{France, 2019 - 2021}
\data{BSc in Common Plan of Engineering, University of Chile.}{Chile, 2017 - 2019}
\end{concept}

\begin{concept}{Work Experience}
\job{Software Engineer Intern at Bigblue}{France, 2021}
\desc{Problem Solving and \textbf{Backend} Development on Golang with FoundationDB on e-commerce logistics.\\ 
Enabled Eco-friendly Deliveries by \textbf{integrating} a Green Carrier to the \textbf{Transportation Management System}.\\%Enabled Spanish Launch by Integrating a Local Carrier
Enabled Invoicing Multiple Countries by \textbf{extending} the \textbf{Billing System} with a per Country Configuration.\\
Reduced Manual Input Errors on Invoices by \textbf{implementing} a \textbf{Semantic Validator} and a \textbf{Duplicate Verifier}.\\
Reduced Billing Processing Time by 50\% by \textbf{automatizing} the \textbf{Batch Import} of Billing Lines.}
%\job{Summer Labor Internship at Amazon}{France, 2020}%Manager Assistant
%\desc{Picking and Packing orders.}
\job{Language Tandem Developer at BdI CentraleSupélec}{France, 2020}
\desc{Organizing multilingual conversation meetings.\\
Matched 47\% more people on by implementing a \textbf{Matching Algorithm} on Python.}%Reduced Computation Time to miliseconds
\job{Research Intern at Sondra Signal Processing Lab}{France, 2020}
\desc{Testing an Order Selection method for \textbf{Image Processing and Finance} on Matlab.\\
Increased Return on Investment on 50\% by using Minimum Variance Portfolio.}
\end{concept}

\begin{concept}{Teaching Assistantships}
\data{\textbf{Combinatorial Algorithms} at University of Chile}{2022}
% \data{\textbf{Mixed Linear Programming} at University of Chile}{2022}
\data{\textbf{Algorithms and Data Structures} at University of Chile}{2018}
\end{concept}

\begin{concept}{Projects}
\data{Binge-Watching Planner website \textbf{Frontend} dev on JavaScript using TMDB API.}{2021}%Binger
\data{Weather Forecast website \textbf{Frontend} dev on JavaScript using OpenWeather API and Node.js.}{2021}%Aurora
%\data{Insurance Revaluation Optimization using \textbf{Data Preprocessing} and \textbf{Parametric Optimization} on Matlab.}{2021}%Generali, CentraleSupélec.
%\data{Noise Control using \textbf{Parametric Optimization} of PDE on Python.}{2020}%Onera and CentraleSupélec.
\data{Film Recommendation website \textbf{Backend} dev with Amazon \textbf{DynamoDB}.}{2020}%Theodo and CentraleSupélec.
\data{\textbf{Propagation Maximization Algorithm} on Python for a Viral Marketing Campaign.}{2020}%Artefact and CentraleSupélec
\data{Geoproximity based \textbf{Social Network} prototype \textbf{Full Stack} dev for Facebook \textbf{Hackathon} Chile.}{2019}%on JavaScript
\data{Tour Guide Robot prototype dev and assembly on Java using Lego Mindstorms.}{2018}%Ruteador
%\data{Matrix Multiplication Optimization.}{2018}
%\data{Huffman Code Compresion.}{2018}
\data{Defective Parts Detector Robot prototype dev assembly on Clang using Arduino.}{2017}
\data{Pokémon Game basic replication on Python.}{2017}
%\data{Expresions and Derivatives Calculator.}{2017}
\end{concept}

\begin{concept}{Honors}
\data{Eiffel Excellence Scholarship granted by the Ministry of Europe and Foreign Affairs.}{2019 - 2021}%Economic support
\data{First Place on Engineering Generation Ranking, University of Chile.}{2018}
%\data{Distinguished Student Recognition at Common Plan of Engineering, University of Chile.}{2017 - 2018}
\data{Andrés Bello Excellence Scholarship granted by the University of Chile.}{2017 - 2022}%Exemption from the annual tuiton fees
%\data{Eighth Place on Engineering Admission Ranking, University of Chile.}{2017}
%\data{Maximal Score on National Mathematics and Science (Physics) University Admission Exams.}{2016}
%\data{Golden Medal at the National Mathematical Olympiad of SOMACHI, Chile.}{2016}
%\data{Best Academic Performance Recognition at Seminario Padre Alberto Hurtado School.}{2016}
%\data{Silver Medal at the National Mathematical Olympiad of SOMACHI, Chile.}{2015}
%\data{Golden Medal at Bío-Bío's Regional Physical Olympiad of SOCHIFI.}{2015}
%\data{Best Score of the level at CEMAT Mathematical Championship of University of Concepción.}{2015}
%\data{Bronze Medal at the National Mathematical Olympiad of SOMACHI, Chile.}{2014}
%\data{Medalla de Oro Olimpiada de Matemáticas de la Universidad del Bío-Bío.}{2014}
%\data{Silver Medal at the National Chemical Olympiad of SCHQ, Chile.}{2014}
%\data{Best Score of the level at CEMAT Mathematical Championship of University of Concepción.}{2014}
%\data{Bronze Medal at the National Mathematical Olympiad of SOMACHI, Chile.}{2013}
%\data{Golden Medal at CEMAT Mathematical Championship of University of Concepción.}{2012}
%\data{Participation at the National Mathematical Olympiad of SOMACHI, Chile.}{2012}
\end{concept}

%Seminars
%\data{Associate and Assistant Professors Training Workshop, University of Chile.}{2018}%FCFM
%\data{Preparation for the National Mathematical Olympiad, University of Concepción Summer School.}{2013}%Distinguished Participation


\vspace{-0.3cm}
\setlength{\columnsep}{4cm}
\begin{multicols}{2}
\begin{map}{Computer Skills}
%\entry{Operative Systems}{Android, iOS, Linux, macOS and Windows.}
%\entry{Writing}{MS Office, Jupyter and \LaTeX.}
\entry{Programming}{Python, Java, Clang and Golang.}
\entry{Web}{HTML, CSS, JavaScript and React.}
\entry{Databases}{DynamoDB, FoundationDB and MySQL.}
\entry{Environments}{VSCode, Command Line and GitHub.}
\end{map}

\begin{map}{Languages}
\entry{English}{Advanced.}
\entry{French}{Advanced.}
\entry{German}{Elementary.}
\entry{Spanish}{Native.}
\end{map}
\end{multicols}
\vspace{-0.3cm}

\begin{map}{Free Time}
\entry{Sports}{Kung Fu (purple belt, mastered stick and saber), Running (finished Paris 10km Run in 52min).}%at Hung Sing Fo Li Cai School, and Gym Training.
%\entry{Volunteering}{Leading visits to Orphanages and Nursing Homes.}%Participation on OPH, constructing houses and implementing social inclusion programs.
\entry{Hobbies}{\textbf{Competitive Programming}, Dancing, Volleyball, Traveling and Practicing other languages.}
%\entry{Social}{Passionate about meeting new and different people.}%Member and Assistant of the Arkontes Catholic Movement
\end{map}

\end{document}